Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em] {\large Yulia Tsvetkov$^\ast$\ Naama Twitto$^\dagger$\ Nathan Schneider$^\ast$\ Noam Ordan$^\dagger$\\ Manaal Faruqui$^\ast$\ Victor Chahuneau$^\ast$\ Shuly Wintner$^\dagger$ \ Chris Dyer$^\ast$}\\[-3em]

### 2013-04-10 paper/paper.tex
some fixes, ducttape shout-out

@@

\begin{table}\centering\small
\begin{tabular}{l@{}c}
\bf Feature & \bf Accuracy (\%) \\
\hline
\feat{POS} & 55.18\\
\feat{FreqChar} & 74.12\\
\feat{CharPrompt} & 65.09\\
\feat{Brown} & 72.26\\
\hline
\feat{DocLen} & 11.81\\
\feat{Punct} & 27.41\\
\feat{Pron} & 22.81\\
\feat{Position} & 53.03\\
\feat{PsvRatio} & 12.26\\
\feat{CxtFxn} \textsmaller{(bigram)} & 62.79\\
\feat{CxtFxn} \textsmaller{(trigram)} & 62.32\\
\feat{Misspell} & 37.29\\
\feat{Restore} & 47.67\\ 
\hline
\feat{CohMark} & 25.71\\
\feat{CohVerb} & 22.85\\
\feat{FxnWord} & 42.47\\
\hline
\end{tabular}
\caption{Independent performance of feature types detailed in \Sref{sec:mainfeats}, \Sref{sec:addfeats} and \Sref{sec:discarded}. 
Accuracy is averaged over 10 folds of cross-validation on the training set.}
\end{table}

\subsection{Main Features}
\label{sec:mainfeats}
We use the following four feature types as the baseline features in our
model.  For features that are sensitive to frequency, we use the log of the (frequency-plus-one) as
the feature's value.  \Tref{tbl:mainfeats} reports the accuracy of using each feature type in
isolation (with 10-fold cross-validation on the training set).

\begin{compactdesc}
\item[\feat{POS}] Part-of-speech $n$-grams.  Features were extracted
  to count every POS 1-, 2-, 3- and 4-gram in each
  document. \ignore{CHI:IN PRP VBD, ARA:NN VBZ, KOR:DT JJ} 
\item[\feat{FreqChar}] Frequent character $n$-grams.  We experimented
  with character $n$-grams: To reduce the number of parameters, we removed features
  only those character $n$-grams that are observed more
  than $5$ times in the training corpus, and $n$ ranges from~1
    to~4. High-weight features include: {\tt TUR:<Turk>}; {\tt ITA:<Ital>}; {\tt JPN:<Japa>}.
\item[\feat{CharPrompt}] Conjunction of the character $n$-gram
  features defined above with the prompt ID.
\item[\feat{Brown}] Substitutions, deletions and insertions counts of Brown cluster 
unigrams and bigrams in each document.\ignore{in top-30 features Brown features occur up to 5 times in 10 out of 11 L1s (all except Arabic)} 
\end{compactdesc}
\noindent
The accuracy of the classifier on the development set using these four
feature types is reported in \tref{tbl:mainfeats}.

@@

\section{Results}
\label{sec:results}
The full model that we used to classify the test set combines all
features listed in \tref{tbl:addfeats}. Using all these features, the
accuracy on the development set is~84.55\%, and on the test set it
is~81.5\%. The values for $\alpha$ and $\tau$ were tuned to optimize development set performance, and found to be $\alpha=5$,$\tau=2$.

@@

\nss{comment on how we did in relation to other task participants? if I were a reader I'd want to know}

>>>>

\nss{comment on how we did in relation to other task participants? as a reader I'd want to know!}

@@

\begin{table}\centering\small
\begin{tabular}{l@{}c}
\bf Feature & \bf Accuracy (\%) \\
\hline
\feat{POS} & 55.18\\
\feat{FreqChar} & 74.12\\
\feat{CharPrompt} & 65.09\\
\feat{Brown} & 72.26\\
\hline
\feat{DocLen} & 11.81\\
\feat{Punct} & 27.41\\
\feat{Pron} & 22.81\\
\feat{Position} & 53.03\\
\feat{PsvRatio} & 12.26\\
\feat{CxtFxn} \textsmaller{(bigram)} & 62.79\\
\feat{CxtFxn} \textsmaller{(trigram)} & 62.32\\
\feat{Misspell} & 37.29\\
\feat{Restore} & 47.67\\ 
\hline
\feat{CohMark} & 25.71\\
\feat{CohVerb} & 22.85\\
\feat{FxnWord} & 42.47\\
\hline
\end{tabular}
\caption{Independent performance of feature types detailed in \Sref{sec:mainfeats}, \Sref{sec:addfeats} and \Sref{sec:discarded}. 
Accuracy is averaged over 10 folds of cross-validation on the training set.}\label{tbl:isolatedfeats}
\end{table}

\subsection{Main Features}
\label{sec:mainfeats}
We use the following four feature types as the baseline features in our
model.  For features that are sensitive to frequency, we use the log of the (frequency-plus-one) as
the feature's value.  \Tref{tbl:isolatedfeats} reports the accuracy of using each feature type in
isolation (with 10-fold cross-validation on the training set).

\begin{compactdesc}
\item[\feat{POS}] Part-of-speech $n$-grams.  Features were extracted
  to count every POS 1-, 2-, 3- and 4-gram in each
  document. \ignore{CHI:IN PRP VBD, ARA:NN VBZ, KOR:DT JJ} 
\item[\feat{FreqChar}] Frequent character $n$-grams.  We experimented
  with character $n$-grams: To reduce the number of parameters, we removed features
  only those character $n$-grams that are observed more
  than $5$ times in the training corpus, and $n$ ranges from~1
    to~4. High-weight features include: {\tt TUR:<Turk>}; {\tt ITA:<Ital>}; {\tt JPN:<Japa>}.
\item[\feat{CharPrompt}] Conjunction of the character $n$-gram
  features defined above with the prompt ID.
\item[\feat{Brown}] Substitutions, deletions and insertions counts of Brown cluster 
unigrams and bigrams in each document.\ignore{in top-30 features Brown features occur up to 5 times in 10 out of 11 L1s (all except Arabic)} 
\end{compactdesc}
\noindent
The accuracy of the classifier on the development set using these four
feature types is reported in \tref{tbl:mainfeats}.\footnote{For experiments in this paper combining multiple types of features, 
we used Jonathan Clark's workflow management tool, \texttt{ducttape} (\url{https://github.com/jhclark/ducttape}).}

@@

\section{Results}
\label{sec:results}
The full model that we used to classify the test set combines all
features listed in \tref{tbl:addfeats}. Using all these features, the
accuracy on the development set is~84.55\%, and on the test set it
is~81.5\%. The values for $\alpha$ and $\tau$ were tuned to optimize development set performance, and found to be $\alpha=5, \tau=2$.

@@
